---
title: "Plotly"
output: 
  html_document:
    toc: true
    toc_float: true
---
# Examples of Plotly

```{r}
library(tidyverse)
library(p8105.datasets)
library(plotly)
library(dplyr)
library(rnoaa)
library(lubridate)
library(ggplot2)
```
I ran the below code to access the rnoaa data as per the p8105 website instructions. I have since commented it out for efficiency.
```{r}
# Get a list of all NY station IDs
#stations <- ghcnd_stations()
#nystationids <-  stations %>% 
#  filter(state == "NY") %>% 
#  distinct(id)

# Pull the desired weather data for all of these stations
#nydat <- meteo_pull_monitors(nystationids$id, 
 #                            date_min = "1981-01-01", 
  #                           date_max = "2010-12-31", 
   #                          var = c("PRCP", "SNOW", "SNWD", "TMAX", "TMIN"))

# Save the resulting data
#save(nystationids, nydat, file = "nynoaadat.RData")
```
Now I will load the data. I will remove rows that do not have values for the core variables "prcp", "snow", "snwd", "tmax" or "tmin."
```{r}
ny_noaa_dropna = ny_noaa %>% drop_na(prcp, snow, snwd, tmax, tmin) %>% janitor::clean_names()
str(ny_noaa_dropna)
#All data are the appropriate formats, except for tmax and tmin, which should be integers. I will convert those.

ny_noaa_clean = ny_noaa_dropna %>% mutate(tmax = as.integer(tmax), tmin = as.integer(tmin))
str(ny_noaa_clean)

ny_noaa_recent_subzero = ny_noaa_clean %>% mutate(year = year(date)) %>% filter (year > 2000, tmin < 0, tmax< 0)
str(ny_noaa_recent_subzero)
#I restricted to recent years and low temperatures to make the dataset more manageable.
```
I will do a scatter plot of precipitation vs. snowfall.
```{r}
ny_noaa_recent_subzero %>% mutate(text_label = str_c("Tmax ºC: ", tmax, "\nTmin ºC: ", tmin)) %>% plot_ly(
    x = ~snow, y = ~prcp, type = "scatter", mode = "markers", color = ~snwd, text = ~ text_label, alpha = 0.5)
```


I will do a box plot of snow depth by weather station id.
```{r}
ny_noaa_recent_subzero %>%  
  plot_ly(y = ~snwd, color = ~id, type = "box", colors = "viridis")
```

I will do a bar plot of weather station id frequency.
```{r}
ny_noaa_recent_subzero %>% count(id) %>% 
  mutate(id = fct_reorder(id, n)) %>% 
  plot_ly(x = ~id, y = ~n, color = ~id, type = "bar", colors = "viridis")
```

